Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions

### 2020-08-10 arxiv/experiments.tex
reorg

%\textbf{The training procedure and baseline.}
For all models, we use a shared module for all tasks and assign a separate output layer on top of the shared module for each task.
The baseline training schedule for MTL is the round-robin training schedule.
%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
We measure the test accuracy of predicting a target task.
We measure computational cost by summing over all epochs the number of samples used in every epoch.

@@

\subsection{Missing Details from the Experiments}\label{app_experiments}

\subsection{Synthetic Settings}\label{app_synthetic}
	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
	\squishlist
		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
	The noise level is $\sigma = 5$.
	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
	This can be achieved similarly by rescaling the task data.
	\squishend

\subsection{Image and Text Classification Settings}\label{app_it}

For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
We run $20$ epochs in total.

\begin{algorithm}[!t]
	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
		\Output The trained modules $B, W_2$ optimized for task $2$.
		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
		\For{$i = 1,\dots, S$}
			\For{$j = 1,\dots, T$}
				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
			\EndFor
			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
				\State \textbf{break}
			\EndIf
		\EndFor
	\end{algorithmic}
\end{algorithm}

>>>>

\paragraph{Synthetic Settings}\label{app_synthetic}
	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
	\squishlist
		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
	The noise level is $\sigma = 5$.
	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
	This can be achieved similarly by rescaling the task data.
	\squishend

\paragraph{Image and Text Classification Settings}\label{app_it}

For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
We run $20$ epochs in total.
%\textbf{The training procedure and baseline.}
For all models, we use a shared module for all tasks and assign a separate output layer on top of the shared module for each task.
The baseline training schedule for MTL is the round-robin training schedule.
%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
We measure the test accuracy of predicting a target task.
We measure computational cost by summing over all epochs the number of samples used in every epoch.

@@
